About

### 2025-02-11 about.qmd
Reformat markdown
To ease change tracking in the future.
Too bad it wasn't done from the
beginning.
Mention all authors and reviewers

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
bibliography: grateful-refs.bib
---

>>>>

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
  - name: "Josephine Zerna"
    orcid: "0000-0003-2892-884X"
  - name: "Christoph Scheffel"
    orcid: "0000-0001-5963-9229"
bibliography: grateful-refs.bib
---

---

This tutorial was created by Florian Kohrt.
It is based on previous work by Josephine Zerna and Christoph Scheffel.
Comments on earlier versions were kindly provided by
Malika Ihle, Florian Pargent, Jonas Hagenberg, Felix Schönbrodt,
and Sarah von Grebmer zu Wolfsthurn.
